Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-07-22 Papers/ms.tex
PSF paragraph

As with any inference, the results presented here may be sensitive to many of
the input modelling assumptions, and a slightly different (yet still
``reasonable'') set of choices might yield different results. For example, if
the density profile of the lens was smooth but not of the SIE form, and the
data were informative enough to show this, the current
model would only be able to explain the data by adding substructures. Hence, an alternative explanation for these results is that, rather than containing a substructure, the density profile of the lens is simply not within
the SIE family. One way of investigating this is to use a different family of
smooth lens models and doing model selection based on the marginal likelihoods.

>>>>

As with any inference, the results presented here may be sensitive to many of
the input modelling assumptions, and a slightly different (yet still
``reasonable'') set of choices might yield different results. For example, if
the density profile of the lens was smooth but not of the SIE form, and the
data were informative enough to show this, the current
model would only be able to explain the data by adding substructures. Hence, an alternative explanation for these results is that, rather than containing a substructure, the density profile of the lens is simply not within
the SIE family. One way of investigating this is to use a different family of
smooth lens models and doing model selection based on the marginal likelihoods.
Another option which we defer to future work is to implement a more flexible
model (such as a concentric mixture of concentric elliptical lenses).

Another potential inadequacy of our model is the assumption that the PSF is
known. In practice, the PSF is often estimated from the image of nearby star(s),
or from theoretical knowledge of the telescope (especially in the case of
space based imaging). However, if the PSF is misspecified, or in fact varies
across the image, this could induce subtle effects in the imaging which our
current model could only explain using substructure.
